---
title: "My Reticulate documentation "
output: pdf_document
params:
    text: "Hi!"
---

```{r}
library(reticulate)
use_python("/usr/local/bin/python3")
reticulate::py_config()
```
```{r}
# `use_virtualenv()` and `use_condaenv()` 
#functions enable specification of versions of Python in virtual or conda environments, fe:
#use_virtualenv("myenv")
```


# Parametric reports (parameters are passed in Reticulate.R file)
```{r}
print(params$text)
```
# Source a file to access a module
```{r}
#reticulate::py_run_file('/Users/dermit01/Documents/python/Chapter_5_Python_R/add.py')
source_python('/Users/dermit01/Documents/python/Chapter_5_Python_R/add.py')
add(5, 10)
suma <-add(5,10)
class(suma)
```
Note that once that is source into R,  the new object is now an R object!

```{r}
py_run_string("print('hi there, printing with py_run_string')")
py_run_string("x=100")
py$x
py_run_string("dic1= {'A':1,'B':2}")
py$dic1
```
# Seamless dictionary creation

Create a dictionary in a more Rish way
```{r}
dic1 = py_dict(keys=c('A','B','C'), values=c(1,2,3))
dic1
dic1$A

py_to_r(dic1)
```
Note that the output looks like the pythonic way to represent a dictionary





```{r}
# import numpy and specify no automatic Python to R conversion
np <- import("numpy", convert = FALSE)
#plt <- import("matplotlib.pyplot",convert = FALSE)
# do some array manipulations with NumPy
a <- np$array(c(1:4))
sum <- a$cumsum()
# convert to R explicitly at the end
py_to_r(sum)

```

```{python libraries}
import pandas as pd
import io
import requests
```

```{python data}
url="https://raw.githubusercontent.com/cs109/2014_data/master/countries.csv"
s=requests.get(url).content
df=pd.read_csv(io.StringIO(s.decode('utf-8')))
print(df.head(3))
```

# Access the python environment with py$

```{r}
library(ggplot2)
ggplot(py$df, aes(x=Region))+
    geom_bar()
```

# Subsetting data in python
#See 43 min https://www.youtube.com/watch?v=U3ByGh8RmSc
```{python}
#to select columns
print(df[["Region"]])
```
Interestingly only 10 rows will be printed. 
```{python}
#to filter row
print(df[df['Region']=="AFRICA"][0:3])
african_regions= df[df['Region']=="AFRICA"].shape[0]
```
Interestingly all rows are printed (I guess is to be explict?) but I can limit the number of printed statement by doing 
subset. Remember python starts with 0 index. 
We can do inline python code with ** py$**. For example the number of afircan regions is `r py$african_regions`

For additional exaples see https://github.com/ttimbers/breast_cancer_predictor/blob/108694bc60bfb4d0be94a93b4d0a0bc1a521b8d3/src/reticulate_fit_breast_cancer_predict_model.R







